Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/impl.tex
proof of Lemma 4

\subsection{Converting IDE Results to IFDS Results}

For each program point $n$, the result of an IFDS analysis gives
a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
pairs each such fact~$d$ with a lattice element $\ell$. Formally,
for an IFDS problem $P$, the result $\resultIFDS$ has type
$N \to D$. Similarly, for an IFDS problem $Q$, the result $\resultIDE$
has type $N \to D \times L$.

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable. Therefore, a result $\rho$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
$\backCC(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell), \forall r\,.\, \ell(r) \neq \top\}$.

@@

\subsection{Implementation of Correlated Calls Micro-Functions}
\otodo{move material from following section here}

>>>>

\subsection{Converting IDE Results to IFDS Results}\label{sec:ideToIfds}

For each program point $n$, the result of an IFDS analysis gives
a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
pairs each such fact~$d$ with a lattice element $\ell$. Formally,
for an IFDS problem $P$, the result $\resultIFDS$ has type
$N \to D$.
\mtodo{Should it be $N^*$ and $\resultIDE(Q)$?}
Similarly, for an IFDS problem $Q$, the result $\resultIDE$
has type $N \to D \times L$.

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\top)\}$.
\mtodo{For the proofs, instead of talking about the transformation for an equivalence-IDE problem,
we should talk about the equivalence transformation for any IDE problem. So we should define
$\backEq(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell),\,\ell\ne\topcc\}$.}

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
$\backCC(\rho) = \lambda n.\{d\mid\rho(n) = (d,\ell), \forall r\,.\, \ell(r) \neq \top\}$.\mtodo{Should it be $\ell(r)\ne\top_T$?}

@@

\subsection{Implementation of Correlated Calls Micro-Functions}
%\otodo{move material from following section here}
